# Sizing Leaflet Markers within sf Polygons

Loading in packages, data, and inscription function.

```{r}
library(sf)
library(ggplot2)

# creates inscribed circle on any polygon
inscribed_circle <- function(poly) {
  # Get centroid of polygon
  centroid <- sf::st_centroid(poly)

  # Get nearest point
  radius <- sf::st_length(sf::st_nearest_points(poly, centroid, pairwise = TRUE))

  # Create circle as a point with a buffer around it
  circle <- sf::st_buffer(centroid, radius)

  return(circle)
}

# loading spatial data
nc <- st_read(system.file("shape/nc.shp", package="sf")) |>
  sf::st_transform("+proj=longlat +datum=WGS84")
```

Selecting the first polygon in the nc dataset.

Determining the distance between the centroid of the polygon and the closest point on the polygon. Creating an inscribed circle with radius equal to this distance and plotting.

Adding a marker that is scaled based on the radius of the inscribed circle. Marker size is in pixels and circle radius is in meters (lat/long calculation). Not sure how to do this conversion.

```{r}
polytest <- nc[1,15]

# creating geometry of inscribed circle
inscribed <- inscribed_circle(polytest)

# calculating size of inscribed polygon
polytest$centroid <- sf::st_centroid(polytest)
iconsize_max <- sf::st_length(sf::st_nearest_points(polytest$geometry,
                                                        polytest$centroid,
                                                        pairwise = TRUE))

# scaling the marker relative to the inscribed polygon size
icons <- leaflet::icons(
  iconUrl = c("https://cdn-icons-png.flaticon.com/512/985/985331.png"),
  iconWidth = iconsize_max/100, # scaling by 100 otherwise icon would not be visible
  iconHeight = iconsize_max/100
)

# Creating leaflet map with polygons and markers
leaflet::leaflet() |>
  leaflet::addPolygons(data = polytest,
              fillOpacity = 0,
              color = "red",
              weight = 1) |>
  leaflet::addPolygons(data = inscribed,
                       fillOpacity = 0,
                       color = "blue",
                       weight = 1) |>
  leaflet::addMarkers(data = polytest$centroid,
                      icon = icons)
```

Selecting another polygon from the nc dataset. The previous method does not work as well for this polygon.

```{r}
polytest <- nc[4,15]

# creating geometry of inscribed circle
inscribed <- inscribed_circle(polytest)

# calculating size of inscribed polygon
polytest$centroid <- sf::st_centroid(polytest)
territory_border <- sf::st_length(sf::st_nearest_points(polytest$geometry,
                                                        polytest$centroid,
                                                        pairwise = TRUE))

# scaling the marker relative to the inscribed polygon size
icons <- leaflet::icons(
  iconUrl = c("https://cdn-icons-png.flaticon.com/512/985/985331.png"),
  iconWidth = territory_border/100,
  iconHeight = territory_border/100
)

# Creating leaflet map with polygons and markers
leaflet::leaflet() |>
  leaflet::addPolygons(data = polytest,
              fillOpacity = 0,
              color = "red",
              weight = 1) |>
  leaflet::addPolygons(data = inscribed,
                       fillOpacity = 0,
                       color = "blue",
                       weight = 1) |>
  leaflet::addMarkers(data = polytest$centroid,
                      icon = icons)
```

Calculating the convex hull of the polygon. Determining the distance between the polygon centroid and the closest point on the hull. It performs better for these decentralized shapes

```{r}
polytest <- nc[4,15]

# creating hull of polygon to better encapsulate region
polytest_hull <- sf::st_convex_hull(polytest)

# creating geometry of inscribed circle
inscribed <- inscribed_circle(polytest_hull)

# calculating size of inscribed polygon
polytest_hull$centroid <- sf::st_centroid(polytest_hull)
territory_border <- sf::st_length(sf::st_nearest_points(polytest_hull$geometry,
                                                        polytest_hull$centroid,
                                                       pairwise = TRUE))

# scaling the marker relative to the inscribed polygon size
icons <- leaflet::icons(
  iconUrl = c("https://cdn-icons-png.flaticon.com/512/985/985331.png"),
  iconWidth = territory_border/100,
  iconHeight = territory_border/100
)

# Creating leaflet map with polygons and markers
leaflet::leaflet() |>
  leaflet::addPolygons(data = polytest,
              fillOpacity = 0,
              color = "red",
              weight = 1) |>
  leaflet::addPolygons(data = inscribed,
                       fillOpacity = 0,
                       color = "blue",
                       weight = 1) |>
  leaflet::addMarkers(data = polytest_hull$centroid,
                      icon = icons)
```

Plotting random polygon from nc dataset with convex hull method. Problem still seems to be the lat/long distance to pixels conversion.

```{r}
polytest <- nc[sample(1:100,1),15]

# creating hull of polygon to better encapsulate region
polytest_hull <- sf::st_convex_hull(polytest)

# creating geometry of inscribed circle
inscribed <- inscribed_circle(polytest_hull)

# calculating size of inscribed polygon
polytest_hull$centroid <- sf::st_centroid(polytest_hull)
territory_border <- sf::st_length(sf::st_nearest_points(polytest_hull$geometry,
                                                        polytest_hull$centroid,
                                                       pairwise = TRUE))

# scaling the marker relative to the inscribed polygon size
icons <- leaflet::icons(
  iconUrl = c("https://cdn-icons-png.flaticon.com/512/985/985331.png"),
  iconWidth = territory_border/100,
  iconHeight = territory_border/100
)

# Creating leaflet map with polygons and markers
leaflet::leaflet() |>
  leaflet::addPolygons(data = polytest,
              fillOpacity = 0,
              color = "red",
              weight = 1) |>
  leaflet::addPolygons(data = inscribed,
                       fillOpacity = 0,
                       color = "blue",
                       weight = 1) |>
  leaflet::addMarkers(data = polytest_hull$centroid,
                      icon = icons)
```
